```{r include = FALSE}
require(rmarkdown); require(knitr); require(sevenbridges); require(readr)

options(max.print = "99"); opts_knit$set(width = 99)
opts_chunk$set(cache=FALSE, tidy=FALSE)

source("~/sbg_auth.R")

```

<hr>

CaVEMan actually needs the reference index and not the reference (?).  But we can attach the reference index as a secondary file to the reference and find the path that way.  Need to ask Erik about this.

It uses outputs from Pindel and ASCAT.

## base command

needs these 3 inputs from other tools

```
-in /datastore/output/${NAME_MT}_vs_${NAME_WT}/pindel/${NAME_MT}_vs_${NAME_WT}.germline.bed  \
-tc $TMP/tum.cn.bed \
-nc $TMP/norm.cn.bed \
```

Prep ASCAT for caveman

```
echo -e "CaVEMan prep: `date`"

set -x
ASCAT_CN="/datastore/output/${NAME_MT}_vs_${NAME_WT}/ascat/$NAME_MT.copynumber.caveman.csv"
perl -ne '@F=(split q{,}, $_)[1,2,3,4]; $F[1]-1; print join("\t",@F)."\n";' < $ASCAT_CN > $TMP/norm.cn.bed
perl -ne '@F=(split q{,}, $_)[1,2,3,6]; $F[1]-1; print join("\t",@F)."\n";' < $ASCAT_CN > $TMP/tum.cn.bed
set +x

```

```{sh base command, eval=FALSE}

caveman.pl
-tb [tumour mutant bam]
-nb [normal wildtype bam]
-r [genome reference index - genome.fa.fai]
-in [pindel .germline.bed]
-tc [tum.cn.bed - from ASCAT]
-nc [norm.cn.bed - from ASCAT]
-t $CPU
-s HUMAN 
-sa GRCh37 
-st WGS
-st genomic
-ig caveman_ucscHiDepth_0.01_merge1000_no_exon.tsv
-b ./ 
-u ./
-o caveman_output

```

<br><br><br><br>

## docker 

The docker conatiner is

``` cgrlab/cgpbox_dev:develop ```

## arguments

```{r arguments, eval=run.mode=="push"}
arguments = list(
  
input(id = "bam", label = "bam", description = "either wildtype or tumour bam", type = "File", prefix = "-i")

)

```


## App ports {.tabset .tabset-fade .tabset-tabs}

### Inputs

```{r inputs, eval=run.mode=="push"}
inputs = list(

input(id = "tumour_bam", label = "tumour_bam", description = "mutant tumour bam", type = "File", prefix = "-tb"),

input(id = "normal_bam", label = "normal_bam", description = "normal wildtype bam", type = "File", prefix = "-nb"),
  
input(id = "genome_reference_index", label = "genome_reference_index", description = "genome_reference_index", type = "File", prefix = "-r"),

input(id = "pindel_germline_bed", label = "pindel_germline_bed", description = "pindel_germline_bed", type = "File", prefix = "-in"),
  
input(id = "ascat_tumour_cn_bed", label = "ascat_tumour_cn_bed", description = "ascat_tumour_cn_bed", type = "File", prefix = "-tc"),
  
input(id = "ascat_normal_cn_bed", label = "ascat_normal_cn_bed", description = "ascat_normal_cn_bed", type = "File", prefix = "-nc")

)

```

### Outputs

```{r output, eval = run.mode=="push"}

outputs = list(

output(id = "std_out", label = "std_out", 
description = "standard output", type = "File...",
metadata = list(org = "cgp"),
glob = Expression(engine = "#cwl-js-engine",
script = "\"*.{out}\"")),
  
output(id = "caveman_output", label = "caveman_output", 
description = "caveman_output", type = "File",
inheritMetadataFrom = "#normal_bam", metadata = list(org = "cgp"),
glob = Expression(engine = "#cwl-js-engine",
script = "\"*.bedpe\""))
  
)


```

## Define Tool Object and Push to Platform {.tabset .tabset-fade .tabset-tabs}
  
### Tool object

```{r 5 create tool object, eval=run.mode=="push"}

tool <- Tool(
id = "CaVEMan", 
label = "CaVEMan",
hints = requirements(docker(pull = "cgrlab/cgpbox_dev:develop"), cpu(1), mem(1000)),
baseCommand = "mkdir caveman_output && CPU=`grep -c ^processor /proc/cpuinfo` && caveman.pl -t $CPU -s HUMAN -sa GRCh37 -st WGS -st genomic -ig caveman_ucscHiDepth_0.01_merge1000_no_exon.tsv -b ./ -u ./ -o caveman_output",
stdout = "std.out",
inputs = inputs,
outputs = outputs)


```

### Push app to sbg platform

```{r 6 push app to sbg, eval=destination=="platform"}

p$app_add("CaVEMan", tool)


```

