```{r include = FALSE}
require(rmarkdown); require(knitr); require(sevenbridges); require(readr)

options(max.print = "99"); opts_knit$set(width = 99)
opts_chunk$set(cache=FALSE, tidy=FALSE)

source("~/cgpbox_cwl_auth.R")

```

<hr>

CaVEMan actually needs the reference index and not the reference (?).  But we can attach the reference index as a secondary file to the reference and find the path that way.

It uses outputs from Pindel and ASCAT.

## base command

```{sh base command, eval=FALSE}

caveman.pl
-r $REF_BASE/genome.fa.fai \
-ig $REF_BASE/caveman/HiDepth.tsv \
-b $REF_BASE/caveman/flagging \
-u $REF_BASE/caveman \
-s '$SPECIES' \
-sa $ASSEMBLY \
-t $CPU \
-st genomic \
-in /datastore/output/${NAME_MT}_vs_${NAME_WT}/pindel/${NAME_MT}_vs_${NAME_WT}.germline.bed  \
-tc $TMP/tum.cn.bed \
-nc $TMP/norm.cn.bed \
-tb $BAM_MT_TMP \
-nb $BAM_WT_TMP \
-o /datastore/output/${NAME_MT}_vs_${NAME_WT}/caveman

```

<br><br><br><br>

## docker 

The docker conatiner is

``` cgrlab/cgpbox_dev:develop ```

## arguments

```{r arguments, eval=run.mode=="push"}
arguments = list(
  
input(id = "bam", label = "bam", description = "either wildtype or tumour bam", type = "File", prefix = "-i")

)

```


## App ports {.tabset .tabset-fade .tabset-tabs}

### Inputs

```{r inputs, eval=run.mode=="push"}
inputs = list(
  
input(id = "normal_bam", label = "normal_bam", description = "normal wildtype bam", type = "File", prefix = "-n"),
  
input(id = "tumour_bam", label = "tumour_bam", description = "mutant tumour bam", type = "File", prefix = "-t"),
  
input(id = "reference", label = "reference", description = "genome reference", type = "File", prefix = "-r"),

input(id = "pindel_bed", label = "pindel_bed", description = "pindel_bed", type = "File", prefix = "-in")



)

```

### Outputs

```{r output, eval = run.mode=="push"}

outputs = list(

output(id = "std_out", label = "std_out", 
description = "standard output", type = "File...",
metadata = list(org = "cgp"),
glob = Expression(engine = "#cwl-js-engine",
script = "\"*.{out}\"")),
  
output(id = "caveman_output", label = "caveman_output", 
description = "caveman_output", type = "File",
inheritMetadataFrom = "#normal_bam", metadata = list(org = "cgp"),
glob = Expression(engine = "#cwl-js-engine",
script = "\"*.bedpe\""))
  
)


```

## Define Tool Object and Push to Platform {.tabset .tabset-fade .tabset-tabs}
  
### Tool object

```{r 5 create tool object, eval=run.mode=="push"}

tool <- Tool(
id = "CaVEMan", 
label = "CaVEMan",
hints = requirements(docker(pull = "cgrlab/cgpbox_dev:develop"), cpu(1), mem(1000)),
baseCommand = "caveman.pl",
stdout = "std.out",
inputs = inputs,
outputs = outputs)


```

### Push app to sbg platform

```{r 6 push app to sbg, eval=destination=="platform"}

p$app_add("CaVEMan", tool)


```

